### 2021-02-15 README.Rmd
tweaked run_cv input
Set default direction = "in" for add_buffer_variable

# Add buffer variable to growth data frame
growth_ex <- growth_ex %>%
  add_buffer_variable(direction = "in", size = comp_dist, region = study_region_ex)

# Optional: Create sf representation of buffer region
buffer_region <- study_region_ex %>% 
  compute_buffer_region(direction = "in", size = comp_dist)
```

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, cv_grid = cv_grid_sf_ex)
```

>>>>

# Add buffer variable to growth data frame
growth_ex <- growth_ex %>%
  add_buffer_variable(size = comp_dist, region = study_region_ex)

# Optional: Create sf representation of buffer region
buffer_region <- study_region_ex %>% 
  compute_buffer_region(size = comp_dist)
```

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, cv_grid = blocks_ex)
```
